---
title: "Week 13 - Class materials"
author: "Jose Luis Rodriguez Gil"
date: "08/12/2020"
output: 
  html_document:
    number_sections: true
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE}
library(tidyverse)
library(janitor)
library(here)
library(lubridate) 

library(gganimate) #annimated (e.g. gif) plots
library(plotly)


```

"No renderer backend detected. gganimate will default to writing frames to separate files
Consider installing:
- the `gifski` package for gif output
- the `av` package for video output
and restarting the R session"


```{r source my theme function}

source(here("functions", "theme_pepe.R"))

```

```{r}

ts_data <- read_csv(here("data", "time_series.csv"))

ts_data <- ts_data %>% 
  mutate(treatment = factor(treatment, levels = c("Low", "Medium", "High")))

```


```{r}

figure_1 <- ts_data %>% 
  filter( compound == "compound_1") %>% 
  ggplot() +
  geom_point(aes(x = samp_date_time, y = concentration, colour = treatment)) +
  theme_pepe() +
  
  # ggannimate sections
  labs(x = NULL,
       y = "Concentration",
       title = 'date: {frame_time}') +
  transition_time(samp_date_time) +
  shadow_mark()

figure_1 <- animate(figure_1, duration = 10, width = 500, height = 500,  renderer = gifski_renderer(loop = TRUE))

figure_1  # NOTE: print(figure_1) works to show it in the viewer, but it wont knit the gif

```

NOTE: You might get this error: "Error in transform_path(all_frames, states[[i]], ease, nframes[i], !!id, : transformr is required to tween paths and lines"


```{r}

anim_save(here("figures", "figure_1.gif"), figure_1)

```



```{r}

figure_2 <- ts_data %>% 
  filter( compound == "compound_1") %>% 
  group_by(treatment, year, month) %>% 
  summarise(mean_concentration = mean(concentration, na.rm = TRUE)) %>% 
  ggplot() +
  geom_line(aes(x = month, y = mean_concentration, colour = treatment)) +
  scale_x_continuous(breaks = seq(1,12, by = 1)) +
  theme_pepe() +
  theme(legend.position = "bottom") +
  labs(x = "Month",
       y = "Concentration") +

  # ggannimate sections
  transition_reveal(along = month)

figure_2 <- animate(figure_2, duration = 10, width = 500, height = 500,  renderer = gifski_renderer(loop = TRUE))

figure_2

```

```{r}

anim_save(here("figures", "figure_2.gif"), figure_2)

```


```{r}
ts_data %>% 
  filter( compound == "compound_1") %>% 
  ggplot() +
  facet_wrap(~month) +
  geom_boxplot(aes(x = treatment, y = concentration)) +
  theme_pepe() 
  #
```

```{r}

figure_3 <- ts_data %>% 
  filter( compound == "compound_1") %>% 
  ggplot() +
  geom_boxplot(aes(x = treatment, y = concentration, colour = treatment)) +
  geom_jitter(aes(x = treatment, y = concentration, colour = treatment), alpha = 0.4) +
  scale_colour_brewer(palette = "Set1") +
  theme_pepe() +
  #
   transition_states(
    month,
    transition_length = 2,
    state_length = 1
  ) +
  labs(x = "Treatment",
       y = "Concentration",
       title = "Month: {closest_state}") +
  enter_fade() +
  exit_shrink() +
  ease_aes('sine-in-out')

figure_3 <- animate(figure_3, duration = 10, width = 500, height = 500,  renderer = gifski_renderer(loop = TRUE))


figure_3  # NOTE: print(figure_3) works to show it in the viewer, but it wont knit the gif

```



```{r}

anim_save(here("figures", "figure_3.gif"), figure_3)

```


# Interactive plots with `plotly`

```{r}

figure_4 <- ts_data %>% 
  filter( compound == "compound_1") %>% 
  ggplot() +
  geom_point(aes(x = samp_date_time, y = concentration, colour = treatment)) +
  theme_pepe()

figure_4

```


```{r}
ggplotly(figure_4)
```








